Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2020-01-03 Ben_Manuscripts/stochastic_transport/Draft.tex
Updates to figures

\usepackage{multirow}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{diagbox}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

@@

%MRS4: Overall - providing a bit gentler easing into the modeling would help. A more clearly articulated overall picture of what the goals of the modeling are.  Does it have to be perfect? Is the main goal just predictive time series, or mechanistic understanding?  Help people a bit more to understand what success or failure would look like.  Help make it clear why the specific models are chosen to investigate. 
%MRS4: To what extent can findings be related back to molecular details?
%MRS4: what are the consequences of the findings?

\title{Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics
and Predicts Long Timescale Behavior in Nanoscale Pores.}
%MRS1: I wonder if ``Times series modeling'' is better?  We should keep thinking about a better term.  Stochastic modeling is such a general term, it encompasses a lot  . . . 
%MRS4: can we turn this into a thesis statement (we find X) rather than a topic statement (we studied X).  Something about the complexity of the models required to get the subdiffusive behavior right?
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \begin{abstract}
  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux in macroscopic length pores. With our first model, based on 
  the anomalous diffusion theory, we show how solute dynamics can be modeled 
  as a fractional diffusion process subordinate to a continuous time random 
  walk. From the MD simulations, we parameterize the distribution of 
  dwell times, hop lengths between dwells and correlation between hops. We 
  explore 2 variations of the anomalous diffusion model. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies 2 sets of parameters based on the solute's radial distance from the
  closest pore center. Our second model, a generalization of Markov state models,
  treats the configurational state of the system as a Markov process, each of
  which has state dependent transport behavior. For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that our models reasonably reproduce
  MSDs calculated from MD simulations. The anomalous diffusion model shows 
  superior predictive performance, in many cases reproducing MD results well
  within error. Finally, we demonstrate how one can use our models in order to
  calculate flux of a given solute across a macroscopic-length pore and, based on 
  those quantities, the membrane's selectivity towards each solute. Overall, this
  work helps connect the relationship between microscopic chemically-dependent
  solute motions and macroscopic membrane performance.

@@

  Highly selective separations membranes are desirable in numerous applications. 
  The ability to efficiently separate ions from saline water sources using membranes 
  has been actively pursued for years in an effort to create potable water for people 
  in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
  municipal water supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides, pharmaceuticals
  and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
  %BJC4: made more general. 
  there is a strong interest in creating breathable fabrics % barriers 
  % to chemical warfare agents
  which selectively allow passage of water vapor.~\cite{mondloch_destruction_2015}
%  The pace at which we achieve these or any other selective separation goals will be 
%  heavily influenced by the quality of insights gained by the modeling approaches above.

@@

  In this work, we use the output of our MD simulations to construct two new classes of 
  mathematical models which aim to predict membrane performance while providing quantitative 
  mechanistic insights. The functional form of these models is driven by mechanistic 
  observations from our previous work and their inputs are parameterized using a 
  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations. The formulation
  of these models requires a dive into stochastically driven processes.

@@

  Three well-known classes of behavior leading to anomalous subdiffusion are 
  continuous time random walks (CTRW), fractional Brownian motion
  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
  These types of motion are frequently used alone or in combination to describe
  single particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014}
  %BJC4: consider rewording sentence below
  A CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories are characterized by sequential independent random draws from 
  each distribution.\cite{montroll_random_1965} FBM is common in crowded,
  viscoelastic environments where each jump comes from a Gaussian distribution
  but is anti-correlated to its previous step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  An RWF is imposed by a system's geometry. Systems with tortuous pathways 
  and dead ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}

@@

  Our second modeling approach applies an extended MSM framework to a relatively 
  small set of known states based on the three previously observed solute trapping mechanisms.  
  Standard MSMs are typically applied to determine equilibrium populations
  of and the kinetics of transitions between various state configurations.~\cite{bowman_using_2009} 
  We extend the framework to include state-dependent fluctuations and correlations in 
  solute position. The magnitudes of a solute's fluctuations from its average trapped 
  position and the degree of correlation with its previous fluctuations is 
  determined by the current state. To distinguish our approach from standard MSMs, we have
  named it the Markov state-dependent dynamical model (MSDDM).

@@

  Finally, we use our most promising model in order to predict solute flux and 
  selectivity in pores of macroscopic length, thus achieving a better understanding
  of macroscopic properties on the basis of microscopic dynamics. We show that 
  anti-correlated solute hopping behavior severely reduces flux relative to 
  uncorrelated behavior. We use the relative solute fluxes to calculate the 
  membrane's selectivity between all pairs of solutes and demonstrate that, when 
  solutes display different degrees of anti-correlated hopping behavior, selectivity
  becomes a function of pore length. With this improved understanding of 
  macroscopic behavior, we can begin to think more critically about how to design 
  membranes in order to selectively pass or reject specific solutes.

@@

  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, but instead it follows a power law of the form:
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 0$ 
  are characteristic of Brownian and superdiffusive motion respectively.

  We analyzed the time-averaged MSD of the simulated trajectories by measuring
  all possible displacements over time lag $\tau$:
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. The ensemble
  MSD is given by:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd}
  \end{equation} 
  In a pure CTRW, for example, the power law distribution of trapping times leads to
  weak ergodicity breaking. The time-averaged MSD is linear while the ensemble averaged
  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
  law trapping behavior, the time between hops diverges so there is no characteristic
  measurement time scale of solute motion. In fact, as measurement time increases, the 
  average MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
  with trapping times on the order of the measurement time get incorporated into the 
  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
  because, compared to the ensemble average, it is a more statistically robust measure
  of the average distance a solute travels over time. Although theoretically possible, we do
  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
  with higher precision using the dwell time distributions as described below.

@@

  % BJC3: Making a logical argument regarding how we estimate H here is important
  % because I haven't seen anyone do it this way.
  sFBM implies that hops are correlated which we describe using the Hurst parameter, $H$. 
  The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
  \begin{equation}
    \gamma(k) = \dfrac{\sigma^2}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
  \label{eqn:fbm_autocorrelation}
  \end{equation}
  where $\sigma^2$ is the variance of the underlying Gaussian distribution from which hops are
  drawn and $k$ is the time lag, or number of increments between hops. The hop autocorrelation
  function is simply Equation~\ref{eqn:fbm_autocorrelation} normalized by the variance. 
  When $H < 0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian motion
  and when $H > 0.5$, one observes positive correlation between hops. There are many methods
  for estimating the Hurst parameter for a time series.~\cite{clegg_practical_2006} It can
  be a difficult task because Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, 
  especially when $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 10 400 ps time lags of the 
  empirically measured autocorrelation function.

@@

  % BJC3: will need to modify this text to reflect different lengths of simulations
  For each solute, we simulated 10,000 anomalous diffusion trajectories of length
  $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
  $T_{sim}$ varied due to differing solute equilibration times. We constructed 
  trajectories by simulating sequences of dwell times and correlated hop lengths
  generated based on parameters randomly chosen from our bootstrapped parameter 
  distributions. We propagated each trajectory until the total time equaled or 
  exceeded $T_{sim}~ \mu$s, then truncated the last data point so that the total 
  time exactly equaled $T_{sim}~ \mu$s since valid comparisons are only possible 
  between fixed length sFBM simulations. 
  % BJC4: removed following sentence because I talk about aging above
  %The power law dwell time behavior gives rise to the aging phenomenon, embodied by a 
  %decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
  We reported the time-averaged MSD after time lags 40\% the length of the trajectory
  with corresponding 95\% confidence intervals.
  When simulating 2 mode models, we determined the state sequence based on random 
  draws weighted by the appropriate row of the probability transition matrix. We 
  drew hops and dwells based on the current state of the system. Since we calculated
  the transition probabilities from a finite data set, they have an associated 
  uncertainty which we 
  %MRS4: not quite sure what you mean by incorporating uncertainty. 
  %BJC4: Added comment about having a finite amount of data with which to create transition matrix. Therefore it is uncertain
  incorporated by re-sampling each row from a two dimensional Dirichlet distribution
  (also called a beta distribution for the 2D case) with concentration parameters 
  defined by the count matrix.~\cite{bacallado_bayesian_2009}

@@

  %We also projected MSDs out to 1 second for each solute. % BJC3:??
  %BJC3: not sure how to cite fbm
  We used the python package \texttt{fbm} to generate exact simulations of FBM and our
  own python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
  \cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
  simulation algorithms for generating FLM trajectories, however, the algorithm
  we used sufficiently approximates draws from the marginal distribution and 
  reasonably approximates the correlation structure. We added an empirical correction
  to enhance the accuracy of the correlation structure (see Section~\ref{S-section:flm_correlation}
  of the Supporting Information for validation of the approach).

@@

  % BJC3: This explanation is in previous section
  %For example, if 
  %we observed state 1 followed by a transition to state 3, we increment the $(1, 3)$ entry
  %of the count matrix by 1. We generate the transition probability matrix from the count matrix by 
  %normalizing the entries in each row so that they summed to unity.

  Adding to the standard MSM framework, we incorporated the dynamics of the solutes
  within each state as well as the dynamics of state transitions, which includes the
  overall configurational state of the solute and it's environments. 
  While MSMs are often used to estimate equilibrium populations of various states, adding 
  state-dependent dynamics allows us to more accurately simulate solute trajectories.
  %BJC4: I said below already
  Hence we distinguish our model from MSMs by referring them as Markov State-Dependent
  Dynamical Models (MSDDMs).

@@

  We use the Hurst parameter to describe this negative time series correlation.
  However, there is not sufficient data to accurately measure a Hurst parameter for 
  each type of transition. We avoided this problem by treating transitions as correlated
  emissions from a single L\'evy stable distribution. This reduces the number of emission
  distributions from 64 to 9 (1 for each of the 8 states and 1 for transitions between states).

@@

  We generated particle trajectories, parameterized with the above models, in order
  to construct a distribution of first passage times across a membrane pore of length $L$.
  We simulated 50000 trajectory realizations, released at the pore entrance ($z=0$). In the case of 
  uncorrelated hops, one can continuously draw from the hop length distribution until 
  $z \geq L$ (or $-L$ for the sake of computational efficiency). The length of time 
  between the last time the particle crossed $z=0$ and the end of the trajectory gives a 
  single passage time. When particle hops are correlated, as they are in all cases of
  this work, we cannot continuously construct the particle trajectories. Rather, we must
  generate trajectories of length $n$ and measure the length of the sub-trajectory 
  which traverses from $0$ to $L$ without becoming negative.
  %BJC4: below is only necessary if you the mean of the distribution exists.
  %It is important to choose a value of $n$ sufficiently
  %large that all trajectories reach $L$, or else the mean first passage time will 
  %be underestimated.

@@

  The evidence suggests that solutes in this system can be well-modeled by subordinated
  fractional Brownian motion. In Figure~\ref{fig:anticorrelated_hops}, we use Urea to
  support this claim. Analogous figures for all other solutes are presented in the Supporting
  Information, Figures~\ref{S-fig:GCL_anticorrelated_hops}--\ref{S-fig:MET_anticorrelated_hops}.
  The solutes clearly perform jumps after periods of relative
  immobility (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
  of jump lengths and power law distribution of dwell times are both characteristic of 
  CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
  anti-correlation between hops suggests a fractional diffusion process is subordinate to the
  CTRW. We believe the subordinated process is FBM because its analytical correlation 
  structure is close to that observed in our simulation (Figure~\ref{fig:hop_acf}). FBM
  is common in crowded viscoelastic environments where motions are highly influenced by
  the motion of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
  %The parameter estimates describing the 1 and 2 mode hop and dwell distributions are 
  %summarized in Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters}.

>>>>

\usepackage{setspace}
\doublespacing
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{diagbox}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

@@

%BJC5: wondering about replacing "Predicts long timescale behavior" with "predicts selectivity"
\title{Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics
and Predicts Long Timescale Behavior in Nanoscale Pores.}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  \begin{abstract}
  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux in macroscopic length pores. With our first model, based on 
  the anomalous diffusion theory, we show how solute dynamics can be modeled 
  as a fractional diffusion process subordinate to a continuous time random 
  walk. From the MD simulations, we parameterize the distribution of 
  dwell times, hop lengths between dwells and correlation between hops. We 
  explore 2 variations of the anomalous diffusion model. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies 2 sets of parameters based on the solute's radial distance from the
  closest pore center. Our second model, a generalization of Markov state models,
  treats the configurational state of the system as a Markov process, each of
  which has state dependent transport behavior. For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that our models reasonably reproduce
  the MSDs calculated from MD simulations. Finally, we demonstrate how one can
  use our models in order to calculate flux of a given solute across a 
  macroscopic-length pore and, based on those quantities, the membrane's selectivity
  towards each solute. Overall, this work helps connect the relationship between
  microscopic chemically-dependent solute motions and macroscopic membrane performance.

@@

  Highly selective separations membranes are desirable in numerous applications. 
  The ability to efficiently separate ions from saline water sources using membranes 
  has been actively pursued for years in an effort to create potable water for people 
  in water-scarce regions.~\cite{werber_materials_2016} Even in relatively safe
  municipal water supplies, there is a need for membranes that can specifically separate
  potentially harmful organic micropollutants such as fertilizers, pesticides, pharmaceuticals
  and personal care products.~\cite{barbosa_occurrence_2016} In the materials industry,
  %BJC5: made more general. 
  there is a strong interest in creating breathable fabrics % barriers 
  % to chemical warfare agents
  which selectively allow passage of water vapor.~\cite{mondloch_destruction_2015}
%  The pace at which we achieve these or any other selective separation goals will be 
%  heavily influenced by the quality of insights gained by the modeling approaches above.

@@

  In this work, we use the output of our MD simulations to construct two classes of 
  mathematical models which aim to predict membrane performance while providing quantitative 
  mechanistic insights. The functional form of these models is driven by mechanistic 
  observations from our previous work and their inputs are parameterized using a 
  substantial amount of data generated by long ($\geq 5~\mu$s) MD simulations. The formulation
  of these models requires a dive into stochastically driven processes.

@@

  Three well-known classes of behavior leading to anomalous subdiffusion are 
  continuous time random walks (CTRW), fractional Brownian motion
  (FBM) and random walks on fractals (RWF).\cite{meroz_toolbox_2015}
  These types of motion are frequently used alone or in combination to describe
  single particle trajectories.~\cite{morrin_three_2018,metzler_anomalous_2014}
  A CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories are characterized by sequential independent random draws from 
  each distribution.\cite{montroll_random_1965} FBM is common in crowded,
  viscoelastic environments where each jump comes from a Gaussian distribution
  but is anti-correlated to its previous step.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  An RWF is imposed by a system's geometry. Systems with tortuous pathways 
  and dead ends cause anti-correlated motion.\cite{meroz_toolbox_2015,neusius_subdiffusion_2008}

@@

  Our second modeling approach applies an extended MSM framework to a relatively 
  small set of known states based on the three previously observed solute trapping mechanisms.  
  Standard MSMs are typically applied to determine equilibrium populations
  of and the kinetics of transitions between various state configurations.~\cite{bowman_using_2009} 
  We extend the framework to include state-dependent fluctuations and correlations in 
  solute position. The magnitude of solute fluctuations from its average trapped 
  position and the degree of correlation with previous fluctuations is 
  determined by the current state. To distinguish our approach from standard MSMs, we have
  named it the Markov state-dependent dynamical model (MSDDM).

@@

  Finally, we use both models in order to predict solute flux and selectivity in 
  pores of macroscopic length, thus achieving a better understanding
  of macroscopic properties on the basis of microscopic dynamics. We show that 
  anti-correlated solute hopping behavior severely reduces flux relative to 
  uncorrelated behavior. We use the relative solute fluxes to calculate the 
  membrane's selectivity between all pairs of solutes and demonstrate that, when 
  solutes display different degrees of anti-correlated hopping behavior, selectivity
  becomes a function of pore length. With this improved understanding of 
  macroscopic behavior, we can begin to think more critically about how to design 
  membranes in order to selectively pass or reject specific solutes.

@@

  Solutes in this system exhibit subdiffusive behavior, a type of anomalous diffusion.
  During an anomalous diffusion process, the mean squared displacement (MSD)
  does not grow linearly with time, but instead it follows a power law of the form:
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha_d}t^{\alpha_d}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha_d$ is the anomalous exponent and $K_{\alpha_d}$ is the generalized 
  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha_d < 1$
  indicates a subdiffusive process, while values of $\alpha_d = 1$ and $\alpha_d > 1$ 
  are characteristic of Brownian and superdiffusive motion respectively.

  We analyzed the time-averaged MSD of the simulated trajectories by measuring
  all possible displacements over time lag $\tau$:
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. Note that only the \textit{ensemble} MSD
  will reproduce the form of Equation~\ref{eqn:msd_form} in all cases. The ensemble
  MSD is given by:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd}
  \end{equation} 
  In a pure CTRW, for example, the power law distribution of trapping times leads to
  weak ergodicity breaking. In this case, the time-averaged MSD is linear while the ensemble averaged
  MSD has the form of Equation~\ref{eqn:msd_form}.~\cite{meroz_toolbox_2015} With power
  law trapping behavior, the time between hops diverges so there is no characteristic
  measurement time scale of solute motion. In fact, as measurement time increases, the 
  average MSD of a CTRW tends to decrease, a phenomenon called aging, because trajectories 
  with trapping times on the order of the measurement time get incorporated into the 
  calculation.~\cite{bel_weak_2005} We chose to analyze just the time-averaged MSD 
  because, compared to the ensemble average, it is a more statistically robust measure
  of the average distance a solute travels over time. Although theoretically possible, we do
  not use the MSD to calculate $\alpha_d$ because we can extract the same parameter 
  with higher precision using the dwell time distributions as described below.

@@

  % BJC3: Making a logical argument regarding how we estimate H here is important
  % because I haven't seen anyone do it this way.
  sFBM implies that hops are correlated which we describe using the Hurst parameter, $H$. 
  The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
  \begin{equation}
    \gamma(k) = \dfrac{\sigma^2}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
  \label{eqn:fbm_autocorrelation}
  \end{equation}
  where $\sigma^2$ is the variance of the underlying Gaussian distribution from which hops are
  drawn and $k$ is the time lag, or number of increments between hops. The hop autocorrelation
  function is simply Equation~\ref{eqn:fbm_autocorrelation} normalized by the variance. 
  When $H < 0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian motion
  and when $H > 0.5$, one observes positive correlation between hops. There are many methods
  for estimating the Hurst parameter for a time series.~\cite{clegg_practical_2006} It can
  be a difficult task because Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, 
  especially when $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 10 0.5 ns time lags of the 
  empirically measured autocorrelation function.

@@

  % BJC3: will need to modify this text to reflect different lengths of simulations
  For each solute, we simulated 1,000 anomalous diffusion trajectories of length
  $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
  $T_{sim}$ varied due to differing solute equilibration times. We constructed 
  trajectories by simulating sequences of dwell times and correlated hop lengths
  generated based on parameters randomly chosen from our bootstrapped parameter 
  distributions. We propagated each trajectory until the total time equaled or 
  exceeded $T_{sim}~ \mu$s, then truncated the last data point so that the total 
  time exactly equaled $T_{sim}~ \mu$s since valid comparisons are only possible 
  between fixed length sFBM simulations. 
  % BJC4: removed following sentence because I talk about aging above
  %The power law dwell time behavior gives rise to the aging phenomenon, embodied by a 
  %decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
  We reported the time-averaged MSD up to a 1000 ns time lag corresponding 95\% confidence
  intervals.

  When simulating 2 mode models, we determined the state sequence based on random 
  draws weighted by the appropriate row of the probability transition matrix. We then
  drew hops and dwells based on the current state of the system. Since we calculated
  the transition probabilities from a finite data set, they have an associated 
  uncertainty which we 
  %MRS4: not quite sure what you mean by incorporating uncertainty. 
  %BJC4: Added comment about having a finite amount of data with which to create transition matrix. Therefore it is uncertain
  incorporated by re-sampling each row from a two dimensional Dirichlet distribution
  (also called a beta distribution for the 2D case) with concentration parameters 
  defined by the count matrix.~\cite{bacallado_bayesian_2009}

@@

  %BJC3: not sure how to cite fbm
  We used the python package \texttt{fbm} to generate exact simulations of FBM and our
  own python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
  \cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
  simulation algorithms for generating FLM trajectories, however, the algorithm
  we used sufficiently approximates draws from the marginal distribution and 
  reasonably approximates the correlation structure on MD simulation timescales. We
  added an empirical correction to enhance the accuracy of the correlation structure
  (see Section~\ref{S-section:flm_correlation} of the Supporting Information for 
  validation of the approach).

@@

  Adding to the standard MSM framework, we incorporated the dynamics of the solutes
  within each state as well as the dynamics of state transitions, which includes the
  overall configurational state of the solute and it's environments. 
  While MSMs are often used to estimate equilibrium populations of various states, adding 
  state-dependent dynamics allows us to simulate solute trajectories.
  %BJC5: I said below already, but I still think it belongs
  Hence why we refer to them as Markov State-Dependent Dynamical Models (MSDDMs).

@@

  We use the Hurst parameter to describe this negative time series correlation.
  However, there is not sufficient data to accurately measure a Hurst parameter for 
  each type of transition. We avoided this problem by combining all distributions 
  associated with state transitions and treating all transitions as correlated
  emissions from a single L\'evy stable distribution. This reduces the number of emission
  distributions from 64 to 9 (1 for each of the 8 states and 1 for transitions between states).

@@

  We generated particle trajectories, parameterized with the above models, in order
  to construct a distribution of first passage times across a membrane pore of length $L$.
  For computational reasons dependent on the model used, we simulated 1000-10000 trajectory
  realizations, released at the pore entrance ($z=0$). In the case of 
  uncorrelated hops, one can continuously draw from the hop length distribution until 
  $z \geq L$ (or $-L$ for the sake of computational efficiency). The length of time 
  between the last time the particle crossed $z=0$ and the end of the trajectory gives a 
  single passage time. When particle hops are correlated, as they are in all cases of
  this work, we cannot continuously construct the particle trajectories. Rather, we must
  generate trajectories of length $n$ and measure the length of the sub-trajectory 
  which traverses from $0$ to $L$ without becoming negative.
  %BJC4: below is only necessary if you the mean of the distribution exists.
  %It is important to choose a value of $n$ sufficiently
  %large that all trajectories reach $L$, or else the mean first passage time will 
  %be underestimated.

@@

  The evidence suggests that solutes in this system can be well-modeled by subordinated
  fractional Brownian motion. In Figure~\ref{fig:anticorrelated_hops}, we use Urea to
  support this claim. Analogous figures for all other solutes are presented in the Supporting
  Information, Figures~\ref{S-fig:GCL_anticorrelated_hops}--\ref{S-fig:MET_anticorrelated_hops}.
  The solutes clearly perform jumps after periods of relative
  immobility (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
  of jump lengths and power law distribution of dwell times are both characteristic of 
  CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
  anti-correlation between hops suggests a fractional diffusion process is subordinate to the
  CTRW. We believe the subordinated process is FBM or FLM because their analytical correlation 
  structures are close to those observed in our simulations (Figure~\ref{fig:hop_acf}). Fractional
  motion is common in crowded viscoelastic environments where movement is highly influenced by
  the movement of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
  %The parameter estimates describing the 1 and 2 mode hop and dwell distributions are 
  %summarized in Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters}.

  \begin{figure}
  \centering
  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
  % /figures/solute_trajectories.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_trajectories.pdf}
  \caption{}\label{fig:solute_trajectories}
  \end{subfigure}
  % Next 3: /figures/sfbm_distributions
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
  \caption{}\label{fig:hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_powerlaw.pdf}
  \caption{}\label{fig:powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{URE_hop_acf.pdf}
  \caption{}\label{fig:hop_acf}
  \end{subfigure}
  \caption{(a) Urea exhibits hops between periods of entrapment, characteristic of a CTRW. 
  (b) The distribution of hop lengths fits well to a Gaussian as well as a more general L\'evy 
  stable distribution. The L\'evy stable distribution does a better job of capturing the 
  heavier tails and increased density near 0. (c) The distribution of dwell times is fit
  well by a power law but it may over-estimate the probability density at long dwell times.
  A power law truncated with an exponential cut-off may better describe the probability of
  long dwell times in our simulations. (d) The hops are negatively correlated to their previous
  hop. In combination, (a) -- (d) support modeling solutes as subordinated fractional Brownian
  and L\'evy motion. The behavior shown by urea in this figure is common to all solutes in this study (see
  Figures~\ref{S-fig:GCL_anticorrelated_hops}--\ref{S-fig:MET_anticorrelated_hops} of the
  Supporting Information).}\label{fig:anticorrelated_hops}
  %MRS4: are there similar figures in the supporting information.
  %BJC4: added
  \end{figure}
